A Context Menu for the Real World: Controlling Physical Appliances Through Head-Worn Infrared Targeting

### 2013-12-10 doc/sigchi14/sigchi14.tex
wrong email address for Ben got fixed

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
% \toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is 	granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org. \\
% {\emph{CHI'14}}, April 26--May 1, 2014, Toronto, Canada. \\
% Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
% DOI string from ACM form confirmation}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)

\toappear{Submitted to CHI2014. Do not cite or distribute without written permission from the authors.}

@@

\numberofauthors{1}
\author{
\alignauthor Yu-Hsiang Chen$^{\dagger}$, Ben Zhang$^{\dagger}$, Claire Tuna$^{\dagger}$, Yang Li$^{\ddagger}$, Edward Lee$^{\dagger}$, Bj\"orn Hartmann$^{\dagger}$ \\
\affaddr{$\dagger$: UC Berkeley EECS \& CITRIS Invention Lab \hspace{0.25in} $\ddagger$: Google Research}\\
\email{sean.yhc@gmail.com, benzh@eecs.berkeley.edy, clairetuna@gmail.com, yangli@acm.org, eal@eecs.berkeley.edu, bjoern@eecs.berkeley.edu}
}
%\author{
% \alignauthor Anonymous for submission
%  \alignauthor 3rd Author Name\\
%    \affaddr{Affiliation}\\
%    \affaddr{Address}\\
%    \email{e-mail address}\\
%    \affaddr{Optional phone number}

>>>>

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
%% \toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org.}
% {\emph{CHI'14}}, April 26--May 1, 2014, Toronto, Canada. \\
% Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
% DOI string from ACM form confirmation}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)

\toappear{}
%Submitted to CHI2014. Do not cite or distribute without written permission from the authors.}

@@

\numberofauthors{1}
\author{
\alignauthor Yu-Hsiang Chen$^{\dagger}$, Ben Zhang$^{\dagger}$, Claire Tuna$^{\dagger}$, Yang Li$^{\ddagger}$, Edward Lee$^{\dagger}$, Bj\"orn Hartmann$^{\dagger}$ \\
\affaddr{$\dagger$: UC Berkeley EECS \& CITRIS Invention Lab \hspace{0.25in} $\ddagger$: Google Research}\\
\email{sean.yhc@gmail.com, benzh@eecs.berkeley.edu, clairetuna@gmail.com, yangli@acm.org, eal@eecs.berkeley.edu, bjoern@eecs.berkeley.edu}
}
%\author{
% \alignauthor Anonymous for submission
%  \alignauthor 3rd Author Name\\
%    \affaddr{Affiliation}\\
%    \affaddr{Address}\\
%    \email{e-mail address}\\
%    \affaddr{Optional phone number}
